Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-07-24 paper-correlations.tex
Fix formatting

\verb+CorrelationFunctions.jl+ is capable to compute all aforementioned correlation
functions. Where possible we provide two implementations for each CF. The first
implementation computes a correlation function in specific predefined directions
(i.e., orientation of test vectors thrown into a sample is fixed) \cite{jiao2014chawla,EPL1}.
There are one predefined direction in 1D case, four directions in 2D case 
(two orthogonal and two diagonal) and thirteen directions in 3D case (three orthogonal, 
six diagonal within each orthogonal plane and four diagonal). The line segment scanning
approach is slower for some CFs but requires much less memory resources. The full map approach
establishes correlations between all points on the image is usually faster. 
Both implementations are contained in \code{Directional} and \code{Map}
modules of the package, correspondingly.

@@

Cluster function can be calculated with the help of previuously described procedures. 
Firstly, we apply an indicator function to an input $A$: $A^{(i)} \xleftarrow{I^{(i)}} A$. When we
label connected components in $A^{(i)}$ using a function that is a part of Julia \code{ImageMorphology.jl} library. 
Labeling algorithm must take into account if the function is calculated with periodic boundary 
conditions \cite{evstigneev2023}. For periodic boundary conditions we implemented our own solution 
as part of the package, as it is absent in the public domain. Then $C_2$
function is a sum of $S_2$ functions calculated for all clusters
separately. Algorithmic complexity of this implementation is $O(MC \log M)$
where $M$ is the number of elements in the input and $C$ is the number of
clusters. The algorithm is then written as:
\begin{algorithmic}[1]
  \Procedure{$C_2$}{$A, phase, periodic$}
  \State $A^{(phase)} \gets I^{(phase)} (A)$
  \State $CC \gets label\_components(A^{(phase)}, periodic)$
  \State $N \gets maximum(CC)$ \Comment Number of connected components
  \State \textbf{return} $\sum\limits_{n=1}^N S_2(CC, n, periodic)$
  \EndProcedure
\end{algorithmic}

>>>>

\code{CorrelationFunctions.jl} is capable to compute all aforementioned
correlation functions. Where possible we provide two implementations for each
CF. The first implementation computes a correlation function in specific
predefined directions (i.e., orientation of test vectors thrown into a sample is
fixed) \cite{jiao2014chawla,EPL1}.  There are one predefined direction in 1D
case, four directions in 2D case (two orthogonal and two diagonal) and thirteen
directions in 3D case (three orthogonal, six diagonal within each orthogonal
plane and four diagonal). The line segment scanning approach is slower for some
CFs but requires much less memory resources. The full map approach establishes
correlations between all points on the image is usually faster.  Both
implementations are contained in \code{Directional} and \code{Map} modules of
the package, correspondingly.

@@

Cluster function can be calculated with the help of previuously described
procedures.  Firstly, we apply an indicator function to an input $A$: $A^{(i)}
\xleftarrow{I^{(i)}} A$. When we label connected components in $A^{(i)}$ using a
function that is a part of Julia \code{ImageMorphology.jl} library.  Labeling
algorithm must take into account if the function is calculated with periodic
boundary conditions \cite{evstigneev2023}. For periodic boundary conditions we
implemented our own solution as part of the package, as it is absent in the
public domain. Then $C_2$ function is a sum of $S_2$ functions calculated for
all clusters separately. Algorithmic complexity of this implementation is
$O(MC\log M)$ where $M$ is the number of elements in the input and $C$ is the
number of clusters. The algorithm is then written as:
\begin{algorithmic}[1]
  \Procedure{$C_2$}{$A, phase, periodic$}
  \State $A^{(phase)} \gets I^{(phase)} (A)$
  \State $CC \gets label\_components(A^{(phase)}, periodic)$
  \State $N \gets maximum(CC)$ \Comment Number of connected components
  \State \textbf{return} $\sum\limits_{n=1}^N S_2(CC, n, periodic)$
  \EndProcedure
\end{algorithmic}
